### 2021-06-18 README.Rmd
fixed spelling in readme

# Fasano Franceschini Test

@@

The fasano.franceschini.test package is an R implementation of the 2-D Kolmogorov-Smirnov (**KS**) two-sample test as defined by Fasano and Franceschini (1987). This is a variant of the 2-D two-sample KS test as originally defined by Peacock (1983).

@@

You can install the released version of fasano.franceschini.test from [CRAN](https://CRAN.R-project.org) with:

@@

And the development version from [GitHub](https://github.com/) with:

>>>>

# Fasano-Franceschini Test

@@

The `fasano.franceschini.test` package is an R implementation of the 2-D Kolmogorov-Smirnov (**KS**) two-sample test as defined by Fasano and Franceschini (1987). This is a variant of the 2-D two-sample KS test as originally defined by Peacock (1983).

@@

<!-- You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://CRAN.R-project.org) with:

@@

And the --> 
You can install the development version of the `fasano.franceschini.test` package from [GitHub](https://github.com/) with:
